---
title: "Exam of course Project: Shiny Application and Reproducible Pitch."
author: "Maxim Kruglov"
date: '30 october 2016 '
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

The app of this presentation was provided on the following link - https://dolfhinm.shinyapps.io/exam_2/

Source code for ui.R and server.R files are available on the GitHub repo: https://github.com/dolfhinm/shiny_app_golton

## Description of app

Web Application functionality

The app show relationship the height of parent and their child.

This is min and max difference beetween their height. This is -7 and 6 cm, respectively.

Also we show evaluation of the child's height and evaluation of the parent's height.

## Dataset of Galton 

Summary of data, which considered in this presentation
```{r cars, echo = TRUE}
library(HistData)
summary(Galton)

```

## PLot of Dataset of Galton

On the plot can see the linear dependence height of the child from the parents height.
```{r pressure}
library(HistData)
library(ggplot2)
plot(Galton)
```


